### 2017-05-01 PAPER/a_Thesis/Masterarbeit.tex
update thesis

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
Quantum cascade lasers (QCLs) are compact, electrically pumped semiconductor devices, which are considered to be promising light sources for far- and mid-infrared regions. Despite its practical significance, generating ultra short pulses from QCLs by mode-locking has achieved only limited success.

There are already several successful experimental attempts by active mode locking so far, but a complete theory system is still not available due to limited knowledge of quite complex mechanism inside cavity, both electrical as well as optical. The purpose of this research is to build a new model based on existed simulation methods to achieve a dynamic modeling of QCLs in time domain, which would help to get a better understanding of its theoretical mechanism and redound to still unresolved issues of the field.

@@

\chapter{Introduction}\pagenumbering{arabic}
QCLs have gained considerable attention since they were first demonstrated at Bell Laboratories in 1994 by Jerome Faist and his colleagues\cite{faist1994quantum}. Due to lack of suitable radiation sources and detectors this region remains one of the least developed spectral regions. Unlike common semiconductor lasers, which utilize electron-hole recombination to realize electromagnetic radiation, QCLs are based on intersub- band transitions in coupled quantum well superlattices\cite{williams2007terahertz}. Benefit from this special mechanism QCLs can utilize the electric power more efficiently and achieve a high output power.

Mode-locking is a technique in optics, which locks multi-mode in resonant laser cavity by enforcing coherence between modes to produce extra short pulse\cite{haus2000mode}. Methods of mode-locking can be simply classified in active mode-locking (AML) and passive mode-locking(PML) depending on whether it is modulated by itself (e.g. absorber) or requires external modulation source (e.g. RF source).

fundamentals of mode-locking knowledge.....

Why conventional methods can not be directly be applied in mode-locking of QCL, analysis !!!

\section{Background and Motivation}
It has been proven to be difficult to directly employ existing techniques from the ultra fast optics community to mode-lock QCLs due to unfavorable physical effects and lack of consolidation theory about its mechanism. Despite various obstacles some clear mode-locking of QCLs has been realized already in the mid-infrared as well as terahertz. All of the attempts are based on active mode-locking, which was recognized as the only viable route to QCL mode locking \cite{revin2016active}. The main idea is to actively mode-lock the QCLs through a modulated injection current with a frequency corresponding to the round-trip frequency $f_{rt}$, which lies in the microwave region extending from around 3 kHz to 300 GHz.

@@

\section{Related work}
different models, advantage and drawbacks

@@

\chapter{Optical Modeling}
Similar with the existing modeling methods, in this model light propagation is described with Maxwell' equation while carrier transportation is determined by Bloch equation. Without regard to lateral non-uniform distribution at boundaries \cite{huang2014non, dhar2015nanoscopic} QCL can be simplified to one-dimensional (1D) structure in the direction of propagation (x axis), which means the electrical components were uniformly distributed throughout the cross-sectional area.

\section{Carrier Transport}
****-->rewrite, give more details about density matrix model

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2]{WFs.pdf}
\caption{Sub-band structure configuration of QCL.}
\label{fig:4Levels}
\end{center}
\end{figure}

@@

\section{Light Propagation}
****-->rewrite, give more explanation for concept polarization P

@@

\chapter{Electrical Modeling}
In the electrical modeling, a modified Transmission Line Method (TLM) was introduced in order to realize a dynamic modeling in time domain. TLM is a very efficient methode which is already widely used for evaluation and dynamic modeling especially in high frequency region where wave nature muss be taken into accout, for example, contact resistance extraction in organic field- effect transistors \cite{xu2010modified}, dynamic modeling of flow in pipelines \cite{johnston2014enhanced} etc. However, in QCLs are transverse magnetic (TM) modes \cite{yan2009directional} while TLM is specially for analysis of transverse electromagnetic (TEM) modes, in which neither electric nor magnetic field in the direction of propagation. The common used metal-metal waveguide (microstrip structure) in QCLs can be regarded as quasi-TEM structure, as the substrate ($ \sim $ 10 um) is quite thin in terms of wavelength (30 mm $ \sim $ 300 mm), and the width of strip conductor is very narrow ($ \sim $ 50 um) in terms of wavelength as well, therefore, a static analysis should be still perfectly adequate in this case.

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.8]{Microstrip.pdf}
\caption{Microstrip structure.}
\label{fig:Microstrip}
\end{center}
\end{figure}

\section{Transmission Line Method}
Transmission line model was created by Oliver Heaviside \cite{heaviside2008electromagnetic} and usually consists of two separated conductors and medium in between (Fig. \ref{fig:TLcircuit}). The conventional TLM is based on Telegrapher's equations (\ref{eq:TLequation1})(\ref{eq:TLequation2}), which describe the evolution of voltage and current both spacial and temporal on an electrical transmission line. These two differential equations contains four distributed components (R', L', G', C') which vary from different transmission lines: R' is distributed resistance of conductors, which is represented by a series resistor in ohms per unit length ($\Omega /m$); L' is distributed inductance resulting from the magnetic field around the line due to self-inductance, which is represented by a series inductor in henries per unit length ($H/m$); G' is distributed conductance of the dielectric material separating the two conductors, which is expressed in siemens per unit length ($S/m$) and represented by a shunt resistor with resistance of 1/G'; C' is distributed capacitance of transmission line, which is represented by a shunt conductor in farads per unit length ($F/m$).

% TL equivalent circuit figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.4]{TLcircuit}
\caption{: An equivalent circuit representation of a differential section of the waveguide with capacitance per unit length C’ and inductance per unit length L’.}
\label{fig:TLcircuit}
\end{center}
\end{figure}
% Transmission line equations
Telegrapher's equations:
\begin{eqnarray}
\frac { \partial v(x,t) }{ \partial x }  &=& -L'\frac { \partial i(x,t) }{ \partial t }-R'i(x,t) \label{eq:TLequation1}\\
\frac { \partial i(x,t) }{ \partial x }  &=& - C'\frac { \partial v(x,t) }{ \partial t }-G'v(x,t) \label{eq:TLequation2}
\end{eqnarray}

In this model, the vertical current component resulting from conductance of active region (n-doped semiconductor) under bias is calculated by current density J(x,t) rather than by distributed conductance G'. Current density J(x,t) is nonuniform and bias dependent, it will be obtained by carrier transmission in optical part. In order to solve these two partial differential equations, finite difference in time domain (FDTD) method is applied which owns second order accuracy.

% Discretisation figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{Discretization}
\caption{Discretization along a staggered temporal and spatial grid.}
\label{fig:Discretisation}
\end{center}
\end{figure}

Following Yee’s staggered grid approximation\cite{yee1966numerical}, voltage and current are discretized with separation of $\Delta x/2$ and $\Delta t/2$ in space and time respectively (See Figure \ref{fig:Discretisation}), which leads to a second-order accurate approximation. Voltage V(x,t) and current I(x,t) samples are then expressed as $ V\big(j\Delta x, (n+\frac{1}{2})\Delta t\big)$ and $ I\big((j+\frac{1}{2})\Delta x, n\Delta t\big)$, where j and n are integers. For reasons of simplicity, in the following text they will be replaced by $ V _{ j }^{ n+\frac{1}{2}}$ and ${ I }_{ j+\frac{1}{2} }^{ n }$. After discretization, the first-order derivative of voltage $\partial V(x,t)$ as well as current $\partial I(x,t)$ in space and time can be simply calculated with central difference method\cite{yang2012central}.

\subsection{Boundary Conditions}
Boundary conditions account for the completeness of differential equations at the boundary. In order to refine the boudaries and avoid hard variation of electrical components, a cascading of $\pi$ networks\cite{orlandi1996fdtd} is introduced for the distributed transmission line by splitting the shunt capacitance and conductance in half with two parallel capacitors and conductors at boundary, which is illustrate in Fig. \ref{fig:BoundaryCondition}.

In active mode-locking, QCL is supplied with source $ {V}_{S} $ which consists of a DC voltage source $ {V}_{DC} $ and an external RF source $ {V}_{RF} $. These two sources are combined through bias-T and the source voltaged can be expressed with $ {V}_{S}=V_{DC}+{V}_{RF} $. As the right side of QCL lefts open, no current component exists at the end node. Consequently, the boundary condition for current is definitely ${I}_{end}^{n} = 0$. Besides, due to existance of wire impedance (50 $\Omega$) there will be voltage drop on it, so the voltage at node 0 is not equal to source voltage $ {V}_{S} $.
% Boundary condition figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.55]{pi_representation}
\caption{Schematic of cascade $\pi$ network representation and Thévenin equivalent circuit.}
\label{fig:BoundaryCondition}
\end{center}
\end{figure}

@@

\subsection{Initial Conditions}
Adequate initial conditions play a important role as well to acquire an accurate solution. However, real initial conditions for electrical distribution are not possible to be determined and verified. They can be only analytically set, which means a reasonable station at very beginning. In this case, supposing that QCL was biased by DC source barely at t$\leqslant 0$, no RF signal has arrived and no lasing yet. The following initial conditions are defined:
\begin{eqnarray}
V_{1}^{0} &=& V_{2}^{0} =...=V_{j}^{0}...=V_{N}^{0} = V_{DC}\\
I_{j+\frac{1}{2}}^{0} &=& I_{S}^{0}\times \frac{N-j}{N} \hspace{3mm} (j=0,1,2...,N-1)
\end{eqnarray}
where, $I_{S}$ is the initial current injection, which can be obtained by integrating J(x,0) over x from optical model. N is the amount of nodes while j integer ranging from 0 to N-1. The initial condition for current is under assumption that at very beginning the current was linearly distributed along active region in x direction.

\section{Estimation of Distributed Components}
The involvement of transmission line requires distributed component parameters. Except for distributed conductance G', which will be calculated in optical part, distributed resistance R', distributed inductance L' as well as distributed capacitance C' still need to be determined. They can be either calcuted as convertial passive components (plane resistor, parallel plane capacitor and inductor), or extracted from S-Parameter, which can be directly measured with network analyser. The former methode is simple and also don't require any extra test, but could lead to large error due to neglection of fringe effect\cite{pillai1970fringing} as well as high frequency influence. The latter is based on experiment, so shows higher accuracy compared with former, but requires extra experiment as well as equipment, which is not always feasible for simulation research.

@@

\subsection{Distributed Capacitance}
The cavity of QC laser is regarded as microstrip line in this case. Quasi-TEM structures, like microstrip, will have frequency dependent impedance and effective dielectric constant. However, if the substrate ($\sim$ 10 um) is thin in terms of wavelength (30 mm $\sim$ 300 mm), and if the strip conductor is very narrow ($\sim$ 50 um) in terms of wavelength, then a static analysis should be perfectly adequate.)

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.5]{Gauss2D.pdf}
\caption{Gauss's 2D equation.}
\label{fig:Gauss2D}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.3]{TL_C.pdf}
\caption{Calculated electrical potential distribution V(y,z) with Matlab.}
\label{fig:Gauss2D}
\end{center}
\end{figure}

@@

${ Q }_{ S }=\oint _{ l }{\varepsilon_{0}\varepsilon_{r}\overrightarrow { E } \cdot d\overrightarrow { r } } $
\subsection{Distributed Inductance}
Ampere’s circuital law

\begin{align}
\nabla \times H=J\\
 \frac { \partial H }{ \partial y } -\frac { \partial H }{ \partial z } =J\\
 \textbf{H}_{P}=\sum _{ i=1 }^{ n }{ \sum _{ j=1 }^{ n }{ \frac { \textbf{I}\times { \textbf{r} }_{ i,j }\Delta S }{ 4\pi { r }_{ i,j }^{ 3 }w }  }  } 
 \end{align}
 where, w is width of lateral cross section and $\textbf{r}$ is vector pointing from the surface element to the observation point P.

 \begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.9]{TL_L(2).pdf}
\caption{The vector $\vec{ r } $ pointing from the surface element to the observation point.}
\label{fig:TL_L(2)}
\end{center}
\end{figure}

The magnetic field at a point $ \textbf{H}_{P}$ results from the magnetic field of each surface element, and can be calculated by adding all these together.

 ...

The energy of inductor $W=\frac{1}{2}LI^{2}=\frac{1}{2}\underset { \Omega  }{\int }{ B H  } d\Omega$

 pictures and calculation....
 use the function quiver of Matlab to plot our vector plot.
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.3]{TL_L.pdf}
\caption{Magnetic feld in cross section y-z plane.}
\label{fig:TL_L}
\end{center}
\end{figure}
\section{Modulation Power}
Not only modulation frequency but also modulation power plays a key role in mode-locking. Even if QCL was modulated at near round trip frequency $f_{rt}$ , it can't be mode locked without enough modulation power. So it is essential to figure out RF power for each simulation in order to analyze the modulation process. The RF source power can be easily calculated as modulation amplitude, signal function (since wave) as well as frequency are all known. But this power is total power and is larger than the power that was injected into QCL. Only the injected RF power will have influence on modulation.

@@

--> rewrite this section 
\chapter{Simulation Results and Comparison with Experiment}
The laser simulated in this work is based on doped $GaAs/Al_{x}Ga_{1-x}As$, which is 3 mm-long, 60 $\mu m$ wide, with height of 10 $\mu m$ metal-metal QCL. It is driven at 77 K and has an emission frequency of 3.8 THz. The average doping level of the active region is $5\times 10^{16} cm^{3}$. Its well and barrier widths are 4.6/9.8/2.6/9.0/4.4/17.6 nm.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{IVCURVE.pdf}
\caption{voltage-current–power characteristics of simulated QCL.}
\label{fig:IVcurve}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.8]{withoutRF.eps}
\caption{Frequency spectrum of simulated QCL.}
\label{fig:withoutRF}
\end{center}
\end{figure}

@@

In order to obtain a accuracy round trip frequency of this QCL, beatnote was used by Fourier transform of its output power. As Fig. \ref{fig:beatnote_noRF} shows,  beatnote of the simulated QCL without modulation, its round trip frequency $f_{rt}$ is around 13.34 GHz.
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.8]{beatnote_noRF.pdf}
\caption{Beatnote of the QCL without modulation.}
\label{fig:beatnote_noRF}
\end{center}
\end{figure}

\section{Simulation Setup}
The source of simulated QCL consists of a DC voltage source and a RF source, which are combined through bias-T. 
% Power calculation of injected RF

replace this ugly picture with that from petar
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.4]{schematicSETUP}
\caption{schematic scheme.}
\label{fig:schematicSETUP}
\end{center}
\end{figure}

@@

\section{Simulation Results}
After 100 round trips simulation, a clear short pulse was observed, as Figure \ref{fig:FWHM} shows, from 4610 to 4690 ps in corresponding to 164 $T_{rt}$. Its Full Width at Half Maximum (FWHM) in this modeling is around 11.6 ps, which shows extremely good agreement with experiment result 11 ps\cite{gellie2010injection}.

\subsection{With different modulation power} 
optimal power injection and comparison with lack of enough RF power as modulation
\subsection{With different modulation frequency} 
"Pulling effect" and locking range

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.9]{FWHM.eps}
\caption{Singel pulse from simulation.}
\label{fig:FWHM}
\end{center}
\end{figure}

\section{Comparison with Experiment}
Describe and argue this simulation results with experiment results from paper "Generating ultrafast pulses of light from qcls"
\chapter{Conclusion}

>>>>

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
Quantum cascade lasers (QCLs) are compact, electrically pumped semiconductor devices, which are considered to be promising light source for mid-infrared and terahertz radiation. Benefit from this special mechanism they can utilize the electric power more efficiently than other diode lasers and achieve a high output power. Despite its practical significance, generating ultra short pulses from QCLs by mode-locking has achieved only limited success in the past decade. In this work, we study the influence of external source on the mode-locking of QCLs. A dynamic model based on Maxwell-Bloch equations as well as transmission line was build to simulate QCLs in time domain. The simulation results were then analyzed and compared with existing experiment results from references to check reliability of the established model.

The purpose of this research is to build a new model based on existed simulation methods to achieve a dynamic modeling of QCLs in time domain, which would help to get a better understanding of its theoretical mechanism and redound to still unresolved issues of the field.

@@

\chapter{Introduction}\pagenumbering{arabic}
The operating principle of QCLs was first proposed by R.F. Kazarinov and R.A. Suris in 1971 \cite{kazarinov1971possibility}. However, due to the complexity of fabrication process until 1994 QCLs was firstly demonstrated at Bell Laboratories by Jerome Faist and his colleagues\cite{faist1994quantum}. They have gained considerable attention afterwards. Unlike common semiconductor lasers, which utilize electron-hole recombination to realize electromagnetic radiation, QCLs are unipolar and their emission is based on intersub- band transitions in coupled quantum well superlattices\cite{williams2007terahertz}. Due to lack of suitable radiation sources and detectors this region remains one of the least developed spectral regions. The occurance of QCLs provides a option as a prominent source to help investigate these regions, because their emission wave length as well gain spectrum can be engineered through various design \cite{gmachl2002ultra}.

To date, only n-type QCLs are successfully realized lasing, the intersubband transmission occurs in conduction band.

Introduction of materials used for QCL

\section{Background and motivation}
There are already several successful experimental attempts by active mode locking so far, but a complete theory system is still not available due to limited knowledge of quite complex mechanism inside cavity, both electrical as well as optical. It has been proven to be difficult to directly employ existing techniques from the ultra fast optics community to mode-lock QCLs due to unfavorable physical effects and lack of consolidation theory about its mechanism. Despite various obstacles some clear mode-locking of QCLs has been realized already in the mid-infrared as well as terahertz. All of the attempts are based on active mode-locking, which was recognized as the only viable route to QCL mode locking \cite{revin2016active}. The main idea is to actively mode-lock the QCLs through a modulated injection current with a frequency corresponding to the round-trip frequency $f_{rt}$, which lies in the microwave region extending from around 3 kHz to 300 GHz.

@@

\section{Related work}
Accompanied with investigation of QCLs in experiments, theoretical modeling techniques are developed step by step.

@@

\chapter{Theory}
\section{Maxwell-Bloch equation}
\section{Transmission line}
Transmission line model was created by Oliver Heaviside \cite{heaviside2008electromagnetic} and usually consists of two separated conductors and medium in between (Fig. \ref{fig:TLcircuit}). The conventional TLM is based on Telegrapher's equations (\ref{eq:TLequation1})(\ref{eq:TLequation2}), which describe the evolution of voltage and current both spacial and temporal on an electrical transmission line. These two differential equations contains four distributed components (R', L', G', C') which vary from different transmission lines: R' is distributed resistance of conductors, which is represented by a series resistor in ohms per unit length ($\Omega /m$); L' is distributed inductance resulting from the magnetic field around the line due to self-inductance, which is represented by a series inductor in henries per unit length ($H/m$); G' is distributed conductance of the dielectric material separating the two conductors, which is expressed in siemens per unit length ($S/m$) and represented by a shunt resistor with resistance of 1/G'; C' is distributed capacitance of transmission line, which is represented by a shunt conductor in farads per unit length ($F/m$).

% TL equivalent circuit figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.4]{images/TLcircuit}
\caption{: An equivalent circuit representation of a differential section of the waveguide with capacitance per unit length C’ and inductance per unit length L’.}
\label{fig:TLcircuit}
\end{center}
\end{figure}
% Transmission line equations
Telegrapher's equations:
\begin{eqnarray}
\frac { \partial v(x,t) }{ \partial x }  &=& -L'\frac { \partial i(x,t) }{ \partial t }-R'i(x,t) \label{eq:TLequation1}\\
\frac { \partial i(x,t) }{ \partial x }  &=& - C'\frac { \partial v(x,t) }{ \partial t }-G'v(x,t) \label{eq:TLequation2}
\end{eqnarray}

\section{Mode-locking}
Mode-locking is a technique in optics, which locks multi-mode in resonant laser cavity by enforcing coherence between modes to produce extra short pulse\cite{haus2000mode}. Methods of mode-locking can be simply classified in active mode-locking (AML) and passive mode-locking(PML) depending on whether it is modulated by itself (e.g. absorber) or requires external modulation source (e.g. RF source).

fundamentals of mode-locking knowledge.....
\chapter{Model}
\section{Optical modeling}
Similar with the existing modeling methods, in this model light propagation is described with Maxwell' equation while carrier transportation is determined by Bloch equation. Without regard to lateral non-uniform distribution at boundaries \cite{huang2014non, dhar2015nanoscopic} QCL can be simplified to one-dimensional (1D) structure in the direction of propagation (x axis), which means the electrical components were uniformly distributed throughout the cross-sectional area.

\subsection{Carrier transport}
****-->rewrite, give more details about density matrix model

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.2]{images/WFs.pdf}
\caption{Sub-band structure configuration of QCL.}
\label{fig:4Levels}
\end{center}
\end{figure}

@@

\subsection{Light propagation}
****-->rewrite, give more explanation for concept polarization P

@@

\section{Electrical modeling}
In the electrical modeling, a modified Transmission Line Method (TLM) was introduced in order to realize a dynamic modeling in time domain. TLM is a very efficient methode which is already widely used for evaluation and dynamic modeling especially in high frequency region where wave nature muss be taken into accout, for example, contact resistance extraction in organic field- effect transistors \cite{xu2010modified}, dynamic modeling of flow in pipelines \cite{johnston2014enhanced} etc. However, in QCLs are transverse magnetic (TM) modes \cite{yan2009directional} while TLM is specially for analysis of transverse electromagnetic (TEM) modes, in which neither electric nor magnetic field in the direction of propagation. The common used metal-metal waveguide (microstrip structure) in QCLs can be regarded as quasi-TEM structure, as the substrate ($ \sim $ 10 um) is quite thin in terms of wavelength (30 mm $ \sim $ 300 mm), and the width of strip conductor is very narrow ($ \sim $ 50 um) in terms of wavelength as well, therefore, a static analysis should be still perfectly adequate in this case.

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.8]{images/Microstrip.pdf}
\caption{Microstrip structure.}
\label{fig:Microstrip}
\end{center}
\end{figure}

\subsection{Transmission line approach}
In this model, the vertical current component resulting from conductance of active region (n-doped semiconductor) under bias is calculated by current density J'(x,t) rather than by distributed conductance G'. Current density J(x,t) is nonuniform and bias dependent, it will be obtained by carrier transmission in optical part.

\begin{eqnarray}
\frac { \partial v(x,t) }{ \partial x }  &=& -L'\frac { \partial i(x,t) }{ \partial t }-R'i(x,t) \label{eq:TLequation3}\\
\frac { \partial i(x,t) }{ \partial x }  &=& - C'\frac { \partial v(x,t) }{ \partial t }-wJ'(x,t) \label{eq:TLequation4}
\end{eqnarray}

\subsubsection{Boundary conditions}
Boundary conditions account for the completeness of differential equations at the boundary. In order to refine the boudaries and avoid hard variation of electrical components, a cascading of $\pi$ networks\cite{orlandi1996fdtd} is introduced for the distributed transmission line by splitting the shunt capacitance and conductance in half with two parallel capacitors and conductors at boundary, which is illustrate in Fig. \ref{fig:BoundaryCondition}.

In active mode-locking, QCL is supplied with source $ {V}_{S} $ which consists of a DC voltage source $ {V}_{DC} $ and an external RF source $ {V}_{RF} $. These two sources are combined through bias-T and the source voltaged can be expressed with $ {V}_{S}=V_{DC}+{V}_{RF} $. As the right side of QCL lefts open, no current component exists at the end node. Consequently, the boundary condition for current is definitely ${I}_{end}^{n} = 0$. Besides, due to existance of wire impedance (50 $\Omega$) there will be voltage drop on it, so the voltage at node 0 is not equal to source voltage $ {V}_{S} $.
% Boundary condition figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.55]{images/pi_representation}
\caption{Schematic of cascade $\pi$ network representation and Thévenin equivalent circuit.}
\label{fig:BoundaryCondition}
\end{center}
\end{figure}

@@

\subsubsection{Initial conditions}
Adequate initial conditions play a important role as well to acquire an accurate solution. However, real initial conditions for electrical distribution are not possible to be determined and verified. They can be only analytically set, which means a reasonable station at very beginning. In this case, supposing that QCL was biased by DC source barely at t$\leqslant 0$, no RF signal has arrived and no lasing yet. The following initial conditions are defined:
\begin{eqnarray}
V_{1}^{0} &=& V_{2}^{0} =...=V_{j}^{0}...=V_{N}^{0} = V_{DC}\\
I_{j+\frac{1}{2}}^{0} &=& I_{S}^{0}\times \frac{N-j}{N} \hspace{3mm} (j=0,1,2...,N-1)
\end{eqnarray}
where, $I_{S}$ is the initial current injection, which can be obtained by integrating J(x,0) over x from optical model. N is the amount of nodes while j integer ranging from 0 to N-1. The initial condition for current is under assumption that at very beginning the current was linearly distributed along active region in x direction.

\subsection{Distributed components}
The involvement of transmission line requires distributed component parameters. Except for distributed conductance G', which will be calculated in optical part, distributed resistance R', distributed inductance L' as well as distributed capacitance C' still need to be determined. They can be either calcuted as convertial passive components (plane resistor, parallel plane capacitor and inductor), or extracted from S-Parameter, which can be directly measured with network analyser. The former methode is simple and also don't require any extra test, but could lead to large error due to neglection of fringe effect\cite{pillai1970fringing} as well as high frequency influence. The latter is based on experiment, so shows higher accuracy compared with former, but requires extra experiment as well as equipment, which is not always feasible for simulation research.

@@

\subsubsection{Distributed capacitance}
The cavity of QC laser is regarded as microstrip line in this case. Quasi-TEM structures, like microstrip, will have frequency dependent impedance and effective dielectric constant. However, if the substrate ($\sim$ 10 um) is thin in terms of wavelength (30 mm $\sim$ 300 mm), and if the strip conductor is very narrow ($\sim$ 50 um) in terms of wavelength, then a static analysis should be perfectly adequate.)

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.5]{images/Gauss2D.pdf}
\caption{Gauss's 2D equation.}
\label{fig:Gauss2D}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.3]{images/TL_C.pdf}
\caption{Calculated electrical potential distribution V(y,z) with Matlab.}
\label{fig:TL_C}
\end{center}
\end{figure}

@@

${ Q }_{ S }=\oint _{ l }{\varepsilon_{0}\varepsilon_{r}\overrightarrow { E } \cdot d\overrightarrow { r } } $
\subsubsection{Distributed inductance}
In order to evaluate the self-inductance of surface metal layer in QCLs, Biot–Savart law \cite{grant2013electromagnetism} is used for computing resultant magnetic field $\textbf{B}$ (SI unit: Tesla) at surrounding which is generated by a steady current $\textbf{I}$. The distributed inductance L is inhere characteristic for a certain metal or wire, and is independent of applied current value.  
\begin{equation}
\textbf{B}=\frac{\mu_{0}}{4\pi}\int _{ C }{ \frac { Id\textbf{l}\times \textbf{r} }{ |\textbf{r}| ^{3}}}
\end{equation}
where $\textbf{l}$ is the current unit length and $\textbf{r}$ is the displacement vector from current unit to the computed point, C is the path that current flows. Boldface denotes that symbols are vector quantities.

In QCLs with metal-metal structure, the thickness of top metal is usually extremely thin which is around 80 nm ($8\times 10^{-8} m$). Therefore, it can be regarded as a current sheet with assumption of no thickness (See Fig. \ref{fig:TL_L(2)}). The magnetic field resulting from a current unit is $d\textbf{B}_{P}=\frac { \mu \textbf{I}\times { \textbf{r}}dS }{ 4\pi w{ r }^{ 3 }}$ while the magnetic field at a point $ \textbf{B}_{P}$ results from the magnetic field of each current unit. Hence, it can be evaluated by adding all these together with superposition principle:
\begin{eqnarray}
 \textbf{B}_{P} &=& \sum _{ i=1 }^{ n }{ \sum _{ j=1 }^{ n }{ \frac { \mu \textbf{I}\times { \textbf{r} }_{ i,j } \Delta S }{ 4\pi w{ r }_{ i,j }^{ 3 } }  }  } \\
 &=& \int _{ -\frac { w }{ 2 }  }^{ \frac { w }{ 2 }  }{ \int _{ -\frac { l }{ 2 }  }^{ \frac { l }{ 2 }  }{ { \frac { \mu { \textbf{I} }\times { { \textbf{r} } }_{ i,j } }{ 4\pi w{ r }_{ i,j }^{ 3 } }  } }  } dxdy \label{eq. TL_L}
 \end{eqnarray}
 where, w is width of lateral cross section and $\textbf{r}$ is vector pointing from the surface element to the observation point P, $\mu$ is permeability depending on given medium and frequency.

 \begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.9]{images/TL_L(2).pdf}
\caption{The vector $\vec{ r } $ pointing from the surface element to the observation point.}
\label{fig:TL_L(2)}
\end{center}
\end{figure}

With formula (\ref{eq. TL_L}) the magnetic field at each point on y-z plane can be solved through either analytical solution or Matlab solution. The energy of inductor can be calculated by following equation:
\begin{equation}
  W=\frac{1}{2}LI^{2}=\frac{1}{2}\underset { \Omega  }{\int }{ B H  } d\Omega
 \end{equation} 
 where $\textbf{H}$ is the auxiliary magnetic field and has a relation $\textbf{B}=\mu \textbf{H}$.

 pictures and calculation....
 use the function quiver of Matlab to plot our vector plot.
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.3]{images/TL_L.pdf}
\caption{Magnetic feld in cross section y-z plane.}
\label{fig:TL_L}
\end{center}
\end{figure}

\chapter{Numerical Treatment}
\section{Discretization}
Following Yee’s staggered grid approximation\cite{yee1966numerical}, voltage and current are discretized with separation of $\Delta x/2$ and $\Delta t/2$ in space and time respectively (See Figure \ref{fig:Discretisation}), which leads to a second-order accurate approximation. Voltage V(x,t) and current I(x,t) samples are then expressed as $ V\big(j\Delta x, (n+\frac{1}{2})\Delta t\big)$ and $ I\big((j+\frac{1}{2})\Delta x, n\Delta t\big)$, where j and n are integers. For reasons of simplicity, in the following text they will be replaced by $ V _{ j }^{ n+\frac{1}{2}}$ and ${ I }_{ j+\frac{1}{2} }^{ n }$. After discretization, the first-order derivative of voltage $\partial V(x,t)$ as well as current $\partial I(x,t)$ in space and time can be simply calculated with central difference method\cite{yang2012central}. 
% Discretisation figure
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{images/Discretization}
\caption{Discretization along a staggered temporal and spatial grid.}
\label{fig:Discretisation}
\end{center}
\end{figure}

magic time step....

In order to solve these two partial differential equations, finite difference in time domain (FDTD) method is applied which owns second order accuracy.

\section{Modulation power}
Not only modulation frequency but also modulation power plays a key role in mode-locking. Even if QCL was modulated at near round trip frequency $f_{rt}$ , it can't be mode locked without enough modulation power. So it is essential to evaluate RF power for each simulation in order to analyze the modulation process. The RF source power can be easily calculated as modulation amplitude, signal function (since wave) as well as frequency are all known. But this power is total power and is larger than the power that was injected into QCL. Only the injected RF power will have influence on modulation.

@@

--> rewrite this section

\chapter{Simulation Results}
The laser simulated in this work is based on doped $GaAs/Al_{x}Ga_{1-x}As$, which is 3 mm-long, 60 $\mu m$ wide, with height of 10 $\mu m$ metal-metal QCL. It is driven at 77 K and has an emission frequency of 3.8 THz. The average doping level of the active region is $5\times 10^{16} cm^{3}$. Its well and barrier widths are 4.6/9.8/2.6/9.0/4.4/17.6 nm.

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.6]{images/IVCURVE.pdf}
\caption{voltage-current–power characteristics of simulated QCL.}
\label{fig:IVcurve}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.8]{images/withoutRF.eps}
\caption{Frequency spectrum of simulated QCL.}
\label{fig:withoutRF}
\end{center}
\end{figure}

@@

In order to obtain a accuracy round trip frequency of this QCL, beatnote was used by Fourier transform of its output power. As Fig. \ref{fig:beatnote_noRF} shows,  beatnote of the simulated QCL without modulation, its round trip frequency $f_{rt}$ is around 13.34 GHz.
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.8]{images/beatnote_noRF.pdf}
\caption{Beatnote of the QCL without modulation.}
\label{fig:beatnote_noRF}
\end{center}
\end{figure}

\section{Simulation setup}
The source of simulated QCL consists of a DC voltage source and a RF source, which are combined through bias-T. 
% Power calculation of injected RF

replace this ugly picture with that from petar
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.4]{images/schematicSETUP}
\caption{schematic scheme.}
\label{fig:schematicSETUP}
\end{center}
\end{figure}

@@

\section{Results}
After 100 round trips simulation, a clear short pulse was observed, as Figure \ref{fig:FWHM} shows, from 4610 to 4690 ps in corresponding to 164 $T_{rt}$. Its Full Width at Half Maximum (FWHM) in this modeling is around 11.6 ps, which shows extremely good agreement with experiment result 11 ps\cite{gellie2010injection}.

\subsection{Modulation with different power} 
optimal power injection and comparison with lack of enough RF power as modulation
\subsection{Modulation with different frequency} 
"Pulling effect" and locking range

\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=0.9]{images/FWHM.eps}
\caption{Singel pulse from simulation.}
\label{fig:FWHM}
\end{center}
\end{figure}

\section{Comparison with experiment}
Describe and argue this simulation results with experiment results from paper "Generating ultrafast pulses of light from qcls"
\chapter{Conclusion}
